Adaptive evolution with aneuploidy and mutation

### 2022-04-03 ms/ms.tex
added vertical lines to diff-tau plots
t
fix a few typos

We assume that if \anwt\ appears in a population of \euwt\ and does not go to extinction then \eumt\ does not appear, and vice versa. Thus, we need to find the minimum of the waiting times for appearance of these genotypes. The minimum of two geometric random variables with rates $p_{2n,2n^*}$ and $p_{2n,2n+1}$ is also a geometric random variable with rate $p_{min} = 1-(1-p_{2n,2n^*})(1-p_{2n,2n+1})$, which is the inverse of the expected waiting time until the first event occurs, $T_{min}=1/p_{min}$.
Given that one of these genotypes appeared, the probability that it was \anwt\ rather than \eumt\ is
$p_A = \frac{p_{2n,2n+1}}{p_{2n,2n^*}+p_{2n,2n+1}}$.

Given a mutation occurs first, the expected adaptation time via the mutation trajectory is 
\begin{equation}\label{eq:T_a} 
T_{M} = T_{min} + \tau_{2n, 2n^*} \;,
\end{equation}
where $\tau_{i, j}$ is the waiting time for fixation of genotype $j$ in a population of genotype $i$, given it starts with a single copy and does not go to extinction by drift.
Given that aneuploidy occurs first,
the expected adaptation time via the aneuploidy trajectory is approximated by
\begin{equation}\label{eq:T_a} 
T_a = T_{min} + T_{2n+1, 2n+1^*} + T_{2n+1^*,2n^*} + \tau_{2n, 2n+1} + \tau_{2n+1, 2n+1^*} + \tau_{2n+1^*, 2n^*} \;.
\end{equation}

>>>>

We assume that if \anwt\ appears in a population of \euwt\ and does not go to extinction then \eumt\ does not appear, and vice versa. Thus, we need to find the minimum of the waiting times for appearance of these genotypes. The minimum of two geometric random variables with rates $p_{2n,2n^*}$ and $p_{2n,2n+1}$ is also a geometric random variable with rate $p_{min} = 1-(1-p_{2n,2n^*})(1-p_{2n,2n+1})$, which is the inverse of the expected waiting time until the first event occurs, $T_{min}=1/p_{min}$.
Given that one of these genotypes appeared, the probability that it was \anwt\ rather than \eumt\ is
$p_a = \frac{p_{2n,2n+1}}{p_{2n,2n^*}+p_{2n,2n+1}}$.

Given a mutation occurs first, the expected adaptation time via the mutation trajectory is 
\begin{equation}\label{eq:T_a} 
T_m = T_{min} + \tau_{2n, 2n^*} \;,
\end{equation}
where $\tau_{i, j}$ is the waiting time for fixation of genotype $j$ in a population of genotype $i$, given it starts with a single copy and does not go to extinction by drift.
Given that aneuploidy occurs first,
the expected adaptation time via the aneuploidy trajectory is approximated by
\begin{equation}\label{eq:T_a} 
T_a = T_{min} + T_{2n+1, 2n+1^*} + T_{2n+1^*,2n^*} + \tau_{2n, 2n+1} + \tau_{2n+1, 2n+1^*} + \tau_{2n+1^*, 2n^*} \;.
\end{equation}
